---
title: "ridgereg"
author: "Brahmantio, B. B. & van Doorn, J."
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{bonuslabgroup8}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(bonuslabgroup8)
library(caret)
library(mlbench)
library(leaps)
```
## Simple Prediction using ridgereg()
This vignette showcases how to do a simple prediction using the `ridgereg()` function.
```{r}
reg1 = ridgereg(Petal.Length~Species, data = iris, lambda = 0.01)
reg1$print()
head(reg1$predict())

```

## Create predictive models
This example uses data from the *BostonHousing* dataset.

```{r}
data("BostonHousing")
```

### Data
The data is split into a training and test set using the caret package, with 80% of the data in the training set and 20% of the data in the test set.

```{r}
set.seed(3456)
trainIndex <- createDataPartition(BostonHousing$medv, p = 0.8, list = FALSE, times = 1)
bhTrain <- BostonHousing[trainIndex,]
bhTest <- BostonHousing[-trainIndex,]
```

## Fit Linear regression and linear regression with forward selection
```{r}
lmFit = caret::train(medv ~ ., data = bhTrain, method = "lm")
lmFit
```

```{r}
lfFit = caret::train(medv ~ ., data = bhTrain, method = "leapForward")
lfFit
```
By looking at the metrics (RMSE, Rsquared, and MAE), we can see that the linear regression performs better than the linear regression with forward selection.

## Fit a ridge regression model
```{r, eval=FALSE}
rr_create = function(){
  rr = list(type = "Regression", library = "bonuslabgroup8", loop = NULL, prob = NULL)
  prm = data.frame(parameter = "lambda", class = "numeric", label = "Lambda")
  rr$parameters = prm
  rrgrid = function(x, y, len = NULL, search = "grid"){
    data.frame(lambda = c(0.5, 0.1, 0.05, 0.01, 0.005, 0.001))
  }
  rr$grid = rrgrid
  rrfit <- function(x, y, wts, param, lev, last, weights, classProbs, ...) { 
    df = as.data.frame(x)
    df$resp = y
    ridgereg(formula = resp ~ ., data = df, lambda = param$lambda, ...)
  }
  rr$fit = rrfit
  rrpred <- function(modelFit, newdata, preProc = NULL, submodels = NULL){
    modelFit$predict(newdata)
  }
  rr$predict <- rrpred
  rrsort <- function(x) x[order(x$lambda),]
  rr$sort <- rrsort
  rr$levels <- function(x) x@levels
  return(rr)
}

rr_method = rr_create()

set.seed(998)
fitControl <- trainControl(method = "repeatedcv",
                           number = 10,
                           repeats = 10)

set.seed(825)
ridgeFit <- train(medv ~.,
                  data = bhTrain,
                  method = rr_method,
                  trControl = fitControl
                     )


# keep getting errors: predictions failed for ... Error in modelFit$predict(newdata) : unused argument (newdata)
```
